Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
fix the O()

Let us consider the number of iterations of the CEGIS loop $n$ required for a specification
$\sigma$.  Since we enumerate candidate programs in order of length, we are always synthesising
programs with length no greater than $K(\sigma)$ (since when we enumerate the first correct program,
we will terminate).  So the space of solutions we search over is the space
of functions computed by $\mathcal{L}$-programs of length no greater than $K(\sigma)$.  Let's
denote this set $\mathcal{L}(K(\sigma))$.
Since there are $O(2^{K(\sigma)}$ \emph{programs} of length $K(\sigma)$ and some functions
will be computed by more than one program, we have $\| \mathcal{L}(K(\sigma)) \| \leq O(2^{K(\sigma)})$.

>>>>

Let us consider the number of iterations of the CEGIS loop $n$ required for a specification
$\sigma$.  Since we enumerate candidate programs in order of length, we are always synthesising
programs with length no greater than $K(\sigma)$ (since when we enumerate the first correct program,
we will terminate).  So the space of solutions we search over is the space
of functions computed by $\mathcal{L}$-programs of length no greater than $K(\sigma)$.  Let's
denote this set $\mathcal{L}(K(\sigma))$.
Since there are $O(2^{K(\sigma)})$ \emph{programs} of length $K(\sigma)$ and some functions
will be computed by more than one program, we have $\| \mathcal{L}(K(\sigma)) \| \leq O(2^{K(\sigma)})$.
